---
title: "Getting Started with grepreaper"
author: "Aarya Pandey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with grepreaper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The **grepreaper** R package aims to simplify advanced file reading tasks by integrating with powerful command-line tools such as `grep`. While R provides several file reading utilities, linking file reading to `grep` offers additional capabilities such as:

-   Counting the number of records before reading the data.

-   Extracting only records that match specific patterns.

-   Reading and aggregating data from multiple files simultaneously.

The package provides wrapper functions to help R users leverage these advanced capabilities without needing extensive command-line knowledge.

This vignette will guide you through using the function `count_rows_with_pattern()` to count rows in the `diamonds` dataset containing a specific pattern.

------------------------------------------------------------------------

## Installation

Currently, you can work with the grepreaper functions by sourcing the code directly. Make sure you have the required packages installed:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("geeky33/grepreaper", build_vignettes = TRUE)

```

------------------------------------------------------------------------

## Usage Example

Below is an example of how to use the `count_rows_with_pattern()` function.

### Load Required Libraries

```{r example1}    
library(data.table)
library(ggplot2)
```

### Example Usage

Count the number of rows in the `diamonds` dataset where the clarity contains the pattern "VS":

``` {r example2}
library(grepreaper)
count_rows_with_pattern("VS")
```

### Explanation

-   The function writes the `diamonds` dataset to a temporary CSV file.

-   It constructs a `grep` command to search for rows matching the specified pattern.

-   The result is read back into R using `fread()`.

-   The number of matching rows is returned.

------------------------------------------------------------------------

## Conclusion

The `count_rows_with_pattern()` function demonstrates how grepreaper simplifies integrating `grep` with R's file reading functions. With further development, the package will include more tools for counting, reading, and aggregating data efficiently.

Stay tuned for more powerful features as grepreaper evolves!
